### 2014-03-08 docs/related-work.tex
Something about FTE.
I think this paragraph is too similar to the introduction of CensorSpoofer.

In response to Internet censorship, many research papers and pragmatic systems
such Freegate, Psiphon, and Lantern have explored the design space of censorship
circumvention. All these schemes are based on a simple idea: deploy a set of
proxies outside the censor's domain, and let the user connect to one of them
which can pass data on to the true destination for the user.

@@

Another path to obfuscation is the steganographic approach: look like
something the censor doesn't block. StegoTorus~\cite{stegotorus}
encodes traffic so as to look like a cover protocol, such as unencrypted HTTP,
using special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a digital stream into an acoustic signal
and sends it over VoIP to a proxy which decodes and forwards it.

% fte

>>>>

% In response to Internet censorship, many research papers and pragmatic systems
% such Freegate, Psiphon, and Lantern have explored the design space of censorship
% circumvention. All these schemes are based on a simple idea: deploy a set of
% proxies outside the censor's domain, and let the user connect to one of them
% which can pass data on to the true destination for the user.

@@

Another path to obfuscation is the steganographic approach: look like
something the censor doesn't block. StegoTorus~\cite{stegotorus}
encodes traffic so as to look like a cover protocol, such as unencrypted HTTP,
using special-purpose encoders.
Code Talker
Tunnel (formerly called SkypeMorph)~\cite{skypemorph} mimics a Skype video call.
FreeWave~\cite{freewave} encodes a digital stream into an acoustic signal
and sends it over VoIP to a proxy which decodes and forwards it.
Format-transforming encryption~\cite{fte} encodes data into strings matching a given regular expression,
enabling it to match a firewall's whitelist or avoid matching its blacklist.
